Spin canonical divisors of log stacky curves

### 2015-06-29 stacky_write_up/spin_cring.tex
subsequent removed

\section{Inductive Lemmas}
\label{sec:induction}
First we present several lemmas which provide the
inductive steps in the proof of the main theorem: Theorem
~\ref{thm:main}. In Subsection ~\ref{ssec:add-points} we prove three lemmas
%Lemma ~\ref {lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3}
which determine the generators and relations of $R_\halfcan=R_{\halfcan' + \frac{\alpha
}{\beta}P}$ from those of $R_{\halfcan'}$, where
%where $X$ is a curve, \todo{Peter: I don't think we need to include this instantiation; $X$ always represents a curve throughout the paper, and we should say something to that effect in the background}
$\halfcan \in \di
X \otimes \BQ $ and  $\frac{\alpha}{\beta} \in \BQ$. 
In
Subsection ~\ref{ssec:raise-orders}, we prove a inductive lemma allowing us to transfer information about the log half canonical ring of a curve with signature $(g; e_1', 
\ldots, e_\tau'; 0)$ to that of a
curve with the same log divisor, the same stacky points, and some subset of the $e_ i'$ incremented by $2$. \todo{Peter: I tried to edit this, but I can't figure out how to make this sentence work well.  There are too many clauses...}
%While Lemma ~\ref{lem:sat-1} may be applied in a fairly general 
%context, Lemma ~\ref{lem:raise-stacky-order} is more specific to 
%half-canonical divisors, although even Lemma
%~\ref{lem:raise-stacky-order} has certain generalizations, as noted
%in Remark ~\ref{rem:raise-fractional-order}

@@

Before proving three lemmas that allow us to inductively add points to the support of a divisor (i.e. $\halfcan\to \halfcan + \frac{\alpha}{\beta}P$), we give a criteria to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m]\to R_D$.  This will be used in the subsequent three lemmas of this section to show, in each case, that a chosen homogeneous ideal is in fact the ideal of relations.\todo{Peter:This last sentence is a little redundant}

@@

To apply the previous lemma, we will need an appropriate monomial ordering.  \todo{Reference the lemma, instead of using previous, since things might get moved around}
The following definition provides the necessary ordering for the subsequent lemma (Lemma \ref{lem:sat-1}).
\begin{defn}
Suppose $\halfcan$ is a divisor of $X$ such that $R_\halfcan$ is generated by $x_1, \ldots x_m$.  Then we have a map $\phi$ from the polynomial ring $k[z_1, \ldots z_m]$ to $R_\halfcan$ given by $z_i\mapsto x_i$. \todo{Do we need to instantiate the $z_i$.  If so, what is the best way to do so.  Saying for indeterminates $z_1, \ldots, z_m$ seems excessive.}  If $P$ is a point in $X$, then $\phi$ defines a graded $P$ reverse lexicographic order {\bf{graded P-revlex}} on $k[z_1, \ldots, z_m]$ as follows: 
If $f=\prod_{i=1}^m {z_i}^{q_i}\ne g=\prod_{i=1}^m {z_i}^{r_i}$, then $f\prec g$ if one of the following holds:
\begin{enumerate}
\item $\deg(f) < \deg(g)$
\item $\deg(f) = \deg(g)$ and $-\ord_P(f) > -\ord_P(g)$
\item $\deg(f) = \deg(g)$, $-\ord_P(f) = -\ord_P(g)$, and $q_i<r_i$ for the largest $i$ such that $q_i\ne r_i$
\end{enumerate}
\end{defn}
\noindent One can easily verify graded $P$-reflex these satisfy the conditions of an ordering.

Before stating the subsequent lemma, which improves O'Dorney's bounds on generators and relations over $\mathbb{P}^1$ \cite[Theorem 8]{dorney:canonical} in the case of effective divisors, we first introduce some of his notation \cite{dorney:canonical}. \todo{Peter: This sentence is very ugly.  On the other hand, I feel we need to say something about O'Dorney before the following definition, or else it is completely unmotivated.  How should we state it better?  Also note that in its current form this sentence neglects that we also extend the result to higher genus; it was too difficult to have this in though.}

>>>>

\section{Inductive Lemmas}
\label{sec:induction}
First we present several lemmas which provide the
inductive steps for the proof of the main theorem: Theorem
~\ref{thm:main}. In Subsection ~\ref{ssec:add-points} we prove three lemmas
%Lemma ~\ref {lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3}
which determine the generators and relations of $R_\halfcan=R_{\halfcan' + \frac{\alpha
}{\beta}P}$ from those of $R_{\halfcan'}$, where
%where $X$ is a curve, \todo{Peter: I don't think we need to include this instantiation; $X$ always represents a curve throughout the paper, and we should say something to that effect in the background}
$\halfcan \in \di
X \otimes \BQ $ and  $\frac{\alpha}{\beta} \in \BQ$. 
In
Subsection ~\ref{ssec:raise-orders}, we prove a inductive lemma allowing us to transfer information about the log half canonical ring of a curve with signature $(g; e_1', 
\ldots, e_\tau'; 0)$ to that of a
curve with the same log divisor, the same stacky points, and some subset of the $e_ i'$ incremented by $2$. \todo{Peter: I tried to edit this, but I can't figure out how to make this sentence work well.  There are too many clauses...}
%While Lemma ~\ref{lem:sat-1} may be applied in a fairly general 
%context, Lemma ~\ref{lem:raise-stacky-order} is more specific to 
%half-canonical divisors, although even Lemma
%~\ref{lem:raise-stacky-order} has certain generalizations, as noted
%in Remark ~\ref{rem:raise-fractional-order}

@@

Before proving three lemmas that allow us to inductively add points to the support of a divisor (i.e. $\halfcan\to \halfcan + \frac{\alpha}{\beta}P$), we give a criteria to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m]\to R_D$.  This will be used in three lemmas of this section to show, in each case, that a chosen homogeneous ideal is in fact the ideal of relations.\todo{Peter:This last sentence is a little redundant}

@@

To apply the previous lemma, we will need an appropriate monomial ordering.  \todo{Reference the lemma, instead of using previous, since things might get moved around}
The following definition provides the necessary ordering for the Lemma \ref{lem:sat-1}.
\begin{defn}
Suppose $\halfcan$ is a divisor of $X$ such that $R_\halfcan$ is generated by $x_1, \ldots x_m$.  Then we have a map $\phi$ from the polynomial ring $k[z_1, \ldots z_m]$ to $R_\halfcan$ given by $z_i\mapsto x_i$. \todo{Do we need to instantiate the $z_i$.  If so, what is the best way to do so.  Saying for indeterminates $z_1, \ldots, z_m$ seems excessive.}  If $P$ is a point in $X$, then $\phi$ defines a graded $P$ reverse lexicographic order {\bf{graded P-revlex}} on $k[z_1, \ldots, z_m]$ as follows: 
If $f=\prod_{i=1}^m {z_i}^{q_i}\ne g=\prod_{i=1}^m {z_i}^{r_i}$, then $f\prec g$ if one of the following holds:
\begin{enumerate}
\item $\deg(f) < \deg(g)$
\item $\deg(f) = \deg(g)$ and $-\ord_P(f) > -\ord_P(g)$
\item $\deg(f) = \deg(g)$, $-\ord_P(f) = -\ord_P(g)$, and $q_i<r_i$ for the largest $i$ such that $q_i\ne r_i$
\end{enumerate}
\end{defn}
\noindent One can easily verify graded $P$-reflex these satisfy the conditions of an ordering.

Before stating the Lemma \ref{lem:sat-1}, which improves O'Dorney's bounds on generators and relations over $\mathbb{P}^1$ \cite[Theorem 8]{dorney:canonical} in the case of effective divisors, we first introduce some of his notation \cite{dorney:canonical}. \todo{Peter: This sentence is very ugly.  On the other hand, I feel we need to say something about O'Dorney before the following definition, or else it is completely unmotivated.  How should we state it better?  Also note that in its current form this sentence neglects that we also extend the result to higher genus; it was too difficult to have this in though.}
